{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-11 thesis/thesis.tex
slight revise concl

For as long as people have written science fiction books,
we have fantasized about robots that can make any complex intuitive decision a human can
in addition to the superhuman arithmetic ability that comes standard with silicon.
Recent trends in machine learning have pursued this aesthetic,
using statistics and pattern recognition to provide convincing output even on never-before-seen inputs,
but few such systems are designed to also alert the user when their output confidence is low.
% appropriate for serving ads (penalty for being wrong -- no click)
% appropriate for drug synthesis (clinical trial vets the output)
% not appropriate for... govt surveillance o.o;
% not appropriate for program verification
As tempting as it is to fantasize an oracle capable of telling for certain whether your program is free of concurrency bugs,
that would be a disservice to both user and machine:
the human skill that artificial intelligence should really try to emulate is
knowing its limits and asking for help when it gets confused.
% ways humans cooperate to make landslide better:
% - test case design incl. preemption sealing
% - abstraction reduction
% - manual inspection of data races
\revision{Here I have demonstrated that stateless model checking can realistically fulfill this ideal,
and I envision a future of concurrency verification where % when
human and program may cooperate to debug and verify even more complex software than ever before.}

>>>>

For as long as people have written science fiction books,
we have fantasized about robots that can make any complex intuitive decision a human can
in addition to the superhuman arithmetic ability that comes standard with silicon.
Recent trends in machine learning have pursued this aesthetic,
using statistics and pattern recognition to provide convincing output even on never-before-seen inputs,
but few such systems are designed to also alert the user when their output confidence is low.
% appropriate for serving ads (penalty for being wrong -- no click)
% appropriate for drug synthesis (clinical trial vets the output)
% not appropriate for... govt surveillance o.o;
% not appropriate for program verification
As tempting as it is to fantasize an oracle capable of telling for certain whether your program is free of concurrency bugs,
that would be a disservice to both user and machine:
the human skill that artificial intelligence should really try to emulate is
knowing its limits and asking for help when it gets confused.
% ways humans cooperate to make landslide better:
% - test case design incl. preemption sealing
% - abstraction reduction
% - manual inspection of data races
\revision{Here I have demonstrated that stateless model checking can realistically fulfill this ideal,
and I envision a future of concurrency verification where % when
human and program may cooperate to debug and verify more complex software than ever before.}
